\begin{thebibliography}{9}

\bibitem{lr}
	Donald Knuth.
	\emph{On the translation of languages from left to right}
	- Information and Control 8, 607-639
	1965.

\bibitem{yacc}
	Stephen Johnson.
	\emph{Yacc: Yet Another Compiler-Compiler}
	- Bell Laboratories, Comp Sci Techn Rep 32. 
	1975

\bibitem{sorcerer}
	Terence Parr.
	\emph{An Overview of SORCERER: A Simple Tree-Parser Generator}
	- International Conference on Compiler Construction,
	1994.

\bibitem{packrat}
	Bryan Ford.
	\emph{Packrat Parsing: Simple, Powerful, Lazy, Linear Time}
	-  International Conference on Functional Programming
	2002.

\bibitem{peg}
	Bryan Ford.
	\emph{Parsing Expression Grammars:
A Recognition-Based Syntactic Foundation
}
	-  POPL’04, January 14–16, 2004.

\bibitem{pred-llk}
	Terence Parr and Russell Quong.
	\emph{Adding semantic and syntactic predicates to LL(k): pred-LL(k)}
	- In Computational Complexity, pages 263–277,
	1994.

\bibitem{parr-thesis}
	Terence Parr.
	\emph{Obtaining Practical Variants of $LL(k)$ and $LR(k)$ for $k>1$ by Splitting the Atomic k-tuple}
	- Thesis submitted to the Faculty of Purdue University
	1993.

\bibitem{ll*}
	Terence Parr, Kathleen Fisher.
	\emph{$LL(*)$: The Foundation of the ANTLR Parser Generator}
	- ACM SIGPLAN Notices, 46, no. 6: 425-436
	2011.

\bibitem{attributed-translations}
	Lewis, P. M. and Rosenkrantz, D. J. and Stearns, R. E.
	\emph{Attributed translations}.
	- Journal of Computer and System Sciences, 
	volume 9,
	December 1974.
	Academic Press

\bibitem{llvm}
	Chris Arthur Lattner.
	\emph{LLVM: An Infrastructure for Multi-Stage Optimization}
	- University of Illinois, 2002.
	
\bibitem{llvm-cgo04}
	Chris Arthur Lattner, Vikram Adve.
	\emph{LLVM: A compilation Framework for Lifelong Program Analysis and Transformation}
	- International Symposium on Code Generation and Optimization, Mart 2004.
	
\bibitem{aosa}
	Amy Brown, Greg Wilson.
	\emph{The Architecture of Open Source Applications}
	- 2011. 11. poglavlje, str. 155-170. 

\bibitem{ssa}
	Ron Cytron, Jeanne Ferrante, Barry K. Rosen, Mark N. Wegman, F. Kenneth Zadeck.
	\emph{Efficiently computing static single assignment form and the control dependence graph}
	- ACM Transactions on Programming Languages and Systems, 1991. 


\bibitem{llvm-doc}
	\emph{LLVM: Documentation}
	- www.llvm.org/docs/

\end{thebibliography}